Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-08 paper/paper.tex
review CEGIS
review Verifying Closed-loop Control Systems

Note that $G(z)$ is a
discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
model of the plant must be discretized to obtain the discrete equivalent
coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization %\red{[pls say how]}
. Although there are several discretization methods available in the literature~\cite{Franklin15}, the
zero-order hold (ZOH) discretization is more suitable for representing the
sampling and holding processes that are typically employed by hybrid
systems~\cite{istepanian2012digital}, i.e. the ZOH discretization models the exact effect of sampling and DAC interpolation over the plant.

\begin{mylemma} \cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH. It is equivalent at the sample times ({\it i.e.} $kT$ to the continuous transfer function $G(s)$ driven by ZOH.  This pulse transfer
function can be computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}

@@

In recent years the development of program synthesis has found many ways to
obtain correct by design programs from high level specifiactions.  One such
approach~\cite{itzhaky2010simple} looks to inductively synthesise invariants
to generate the desired programs.  Since these digital programs are already
constrained by designed to factors such as FWL, these approaches are ideal
for the synthesis of parametric controllers. 
In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the
synthesis of switching controllers for stabilizing continuous-time plants
with polynomial dynamics.  The work extends to its application on affine
systems, finding its major challenge in the hardness of solving linear
arithmetic on present SMT solvers.  Since this approach uses switching
states instead of linear dynamics in the digital controller, it entirely
circumvents the FWL problem.  It is also not suitable for the kind of
control we seek to synthesise.  What is needed in this regard is the
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from \cite{daes20161} whilst enhancing the
procedure by evaluating the quantaization effects of the Hardware interfaces
(ADC/DAC) to obtain an accurate discrete time FWL representation of the
continuous dynamics.

>>>>

Note that $G(z)$ is a
discrete model of a real (and continuous) plant, {\it i.e.}, a continuous
model of the plant must be discretized to obtain the discrete equivalent
coefficients $b$ and $a$~\cite{Astrom08} via ZOH discretization.
Although there are several discretization methods available in the literature~\cite{Franklin15}, the
zero-order hold (ZOH) discretization is more suitable for representing the
sampling and holding processes that are typically employed by hybrid
systems~\cite{istepanian2012digital}, {\it i.e.}, the ZOH discretization models 
the exact effect of sampling and DAC interpolation over the plant.

\begin{mylemma} \cite{astrom1997computer}
%
The pulse transfer function $G(z)$ is a z-domain model that relates the output sampled by a ADC and the digital input provided by ZOH. It is equivalent at the sample times ({\it i.e.}, $kT$ to the continuous transfer function $G(s)$ driven by ZOH).  This pulse transfer
function can be computed as
%
\begin{equation}
\label{eq:pulsetf}
G(z,T) = (1-z^{-1})\mathcal{Z}\left\lbrace{\mathcal{L}^{-1}\left\lbrace{\frac{G(s)}{s}}\right\rbrace_{t=kT}}\right\rbrace.
\end{equation}

@@

In recent years the development of program synthesis has found many ways to
obtain correct by design programs from high-level specifications.  One such
approach~\cite{itzhaky2010simple} looks to inductively synthesise invariants
to generate the desired programs.  Since these digital programs are already
constrained by designed to factors such as FWL, these approaches are ideal
for the synthesis of parametric controllers. 
In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS for the
synthesis of switching controllers for stabilizing continuous-time plants
with polynomial dynamics.  The work extends to its application on affine
systems, finding its major challenge in the hardness of solving linear
arithmetic on present SMT solvers.  Since this approach uses switching
states instead of linear dynamics in the digital controller, it entirely
circumvents the FWL problem.  It is also not suitable for the kind of
control we seek to synthesise.  What is needed in this regard is the
combination of a synthesis engine with a control verification tool that
addresses the challenges presented here in the form of FWL effects and
stability measures for LTI SISO controllers.  We take the former
from~\cite{DBLP:conf/lpar/DavidKL15} and the latter from \cite{daes20161} whilst enhancing the
procedure by evaluating the quantaization effects of the Hardware interfaces
(ADC/DAC) to obtain an accurate discrete time FWL representation of the
continuous dynamics.
